---
title: "Microbiome Manuscript Metaproteome Codebook"
author: "Kenzie"
date: "January 14, 2020"
output: pdf_document
---
setwd("K:/Kenzie computer/WORK/neovaginas/2019 analysis/BMC Microbiome Submission/Revisions/Supporting Materials")
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Metaproteomic analysis of neovaginal and cis vaginal samples
### Birse et al. "The neovaginal microbiome of transgender women post-gender reassignment surgery"

--------------
This document contains a subset of the data processing and figure generation conducted in this study.

All data to reproduce this analysis can be found here: `https://github.com/kmbirse/Birse_etal_Neovaginal-Microbiome`

Load the necessary libraries: Flexibly Reshape Data: A Reboot of the Reshape Package, Community Ecology Package, and Create Elegant Data Visulisations Using the Grammer of Graphics

```{r}
library(reshape2)
library(vegan)
library(ggplot2)

```

Load and view the metaproteomic dataset in long format

```{r}
df = read.csv("Bacterial proteins.csv")
View(df)
```

Our goal is to: 

1. Bin the data at the genus level
2. Convert to a wide format. 
3. Convert to proportions.
4. Generate a stacked bar plot.

##Step 1

Bin at genus level

```{r}
aggdata = aggregate(df$Normalized.Total.Spectral.Count, list(df$SubjectID, df$Genus), FUN = sum) #sum of all proteins measured per genus
colnames(aggdata) = c("SubjectID", "Genus", "Normalized Total Spectral Count")
View(aggdata)

```

##Step 2

Convert to wide format

```{r}
wide = dcast(aggdata, Genus~SubjectID, value.var = "Normalized Total Spectral Count")
wide[is.na(wide)] = 0 #changes NA to 0
View(wide)

write.csv(wide, "Bacterial Genera spectral counts.csv")

```

Note: There are 32 cis vaginal samples, 7 rectal samples, and 5 neovaginal samples. There are 39 taxa (38 genera + undistinguishable)

##Step 3

Convert spectral counts to proportions

#Delete first column of numbers in excel from "Bacterial Genera spectral counts.csv" and read back in

```{r}
w=read.csv("Bacterial Genera spectral counts.csv", header = T, row.names = 1)

source("PPFunctions_noCLRS_edited theme_KB_shanhedit.R") # functions for obtaining proportions, generating painter's plots, and hiearchical clustering
source('K:/bacteria_pplot_clrs_v2.R') #function for desired colours
prop = getProp(w)

View(prop)

write.csv(prop, "Bacterial Genera Proportions wide.csv")

```

```
##Step 4 Generate a stacked bar plot

##FIGURE 1B Example

```{r}
propall=prop
png("Neovagina all plots.png", width = 10, height = 8, units = "in", res = 300)
PPlot(propall, subject_numbers = F)
dev.off()

png("Neovagina dendrogram_propall.png", width =10, height = 8, units='in', res=300)
plotClust(propall, subject_numbers = F)
dev.off()

png("Neovagina shannonH_propall.png", width = 10, height = 8, units="in", res=300)
shanH(propall)
dev.off()

s <- diversity(t(propall), "shannon")
d <- data.frame(1:length(s), s)
colnames(d) <- c("Subject", "S")

write.csv(d, "ShannonH values.csv")
```

